Implementing Capon Beamforming on the GPU for Real Time Cardiac Ultrasound Imaging

### 2012-12-14 HRUIonGPU/jrnl_article.tex
back on writing for uffc

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=2in]{gfx/das.png} \label{fig:phantomDAS}}
\hfil
\subfloat[]{\includegraphics[width=2in]{gfx/capon.png} \label{fig:phantomMV}}
\hfil
\subfloat[]{\includegraphics[width=2in]{gfx/capon_bs.png} \label{fig:phantomBS}}}
\caption{Simulated phantom containing one bright and one dark "cyst" and two point targets in speckle. The simulation was done using Field II with a 2.5MHz, $\lambda/2$ and 64 elements array. a) Delay-and-sum with uniform weights. b) Capon ($L=32, K=2, d=0.1$) c) Beamspace Capon ($L=32, K=2, N_b=3, d=0.01$).}
\label{fig:phantom}
\end{figure*}

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=2in]{gfx/das_invivo.png} \label{fig:invivoDAS}}
\hfil
\subfloat[]{\includegraphics[width=2in]{gfx/capon_invivo.png} \label{fig:invivoMV}}
\hfil
\subfloat[]{\includegraphics[width=2in]{gfx/capon_bs_invivo.png} \label{fig:invivoBS}}}
\caption{\textit{In-vivo} harmonic cardiac ultrasound image acquired using a 3.5MHz, 64 elements phased array.  a) Delay-and-sum with uniform weights. b) Capon ($L=32, K=2, d=0.1$) c) Beamspace Capon ($L=32, K=2, N_b=3, d=0.01$).}
\label{fig:invivo}
\end{figure*}

>>>>

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=2.3in]{gfx/das.png} \label{fig:phantomDAS}}
\hfil
\subfloat[]{\includegraphics[width=2.3in]{gfx/capon.png} \label{fig:phantomMV}}
\hfil
\subfloat[]{\includegraphics[width=2.3in]{gfx/capon_bs.png} \label{fig:phantomBS}}}
\caption{Simulated phantom containing one bright and one dark "cyst" and two point targets in speckle. The simulation was done using Field II with a 2.5MHz, $\lambda/2$ and 64 elements phased array. Dynamic range is -30dB to 30dB with mean value represented as 0dB. a) Delay-and-sum with uniform weights. b) Capon ($L=32, K=2, d=0.1$) c) Beamspace Capon ($L=32, K=2, N_b=3, d=0.01$).}
\label{fig:phantom}
\end{figure*}

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=2.3in]{gfx/das_invivo.png} \label{fig:invivoDAS}}
\hfil
\subfloat[]{\includegraphics[width=2.3in]{gfx/capon_invivo.png} \label{fig:invivoMV}}
\hfil
\subfloat[]{\includegraphics[width=2.3in]{gfx/capon_bs_invivo.png} \label{fig:invivoBS}}}
\caption{\textit{In-vivo} harmonic cardiac ultrasound image acquired using a 3.5MHz, 64 elements phased array. Number of receive beams for the $70\degree$ sector is 98. Dynamic range is -20dB to 20dB with mean value represented as 0dB. a) Delay-and-sum with uniform weights. b) Capon ($L=32, K=2, d=0.1$) c) Beamspace Capon ($L=32, K=2, N_b=3, d=0.01$).}
\label{fig:invivo}
\end{figure*}
